Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
d

@@

df <- df0 %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1640 & publication_year <= 1828)
places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
df$publication_place[!df$publication_place %in% places] <- "Other"
df <- subset(df, !is.na(df$publication_place))
#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
library(reshape2)
library(magrittr)
library(dplyr)
library(tidyr)

>>>>

df <- df0 %>% filter(catalog == catalogue)%>%
        filter(publication_year >= 1640 & publication_year <= 1828)
places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
df$publication_place[!df$publication_place %in% places] <- "Other"
df <- subset(df, !is.na(df$publication_place))
#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
library(reshape2)
library(magrittr)
library(dplyr)
library(tidyr)

@@
